---
title: "Functions"
author: "D&D"
date: "May 25, 2017"
output: html_document
---

<div style="text-align: left">
The data we used was collected by survey and input through a google form, </br>
because of the fact that it was entered as strings by several people we had to reenter ,</br>
some of it as well as define some of the columns, as either string or numeric in MS Excel. </br>
once loaded we named it:

```{r}
library(shiny)
library(shinythemes)
library(markdown)
library(curl)
library(ggplot2)
library(dplyr)
library(leaflet)
library(reshape2)

# setwd("C:\\Users\\Dror Bogin\\Desktop\\University\\Geogeraphy\\seminar_diana\\app_test")

socio <- read.csv("SOCIO.csv", header = TRUE, stringsAsFactors = TRUE)
physical <- read.csv("PHYSICAL.csv", header = TRUE, stringsAsFactors = TRUE)
physical <- physical[,1:7]
pay <- read.csv("PAY_EILAT.csv", header = TRUE, stringsAsFactors = TRUE)

names(socio) <- c("ID", "num_res", "subten", "sex_1","age_1", "edu_1", "work_1","sex_2","age_2", "edu_2", "work_2", "kids_num","kids_age", "income", "notes")
names(physical) <- c("ID","glaz", "shutter", "hou_size","hea", "mon_hea", "dur_hea")
names(pay) <- c("ID","AM_FIRST_PAY","START_FIRST_PAY","END_FIRST_PAY","AM_SEC_PAY","START_SEC_PAY","END_SEC_PAY","AM_THIRD_PAY","START_THIRD_PAY","END_THIRD_PAY")
```

We then calculated the elecricty consumption per household by the ammount they payed, </br>
this was done using Dplyr's mutate function while considering each possible date for</br>
electric bill as the fixed payment changes between months while the variable payment is</br>
allways an added 17%, here is and example for one of the consumption in KW columns created. </br>
a total of three such columns were created:

```{r}
pay <- mutate(pay, kw1 = if_else(pay$START_FIRST_PAY == "2016-07-01", (((pay$AM_FIRST_PAY - 26.89)-((pay$AM_FIRST_PAY*100/117)*0.17))/0.4558),if_else(pay$START_FIRST_PAY == "2016-09-01", (((pay$AM_FIRST_PAY - 25.07)-((pay$AM_FIRST_PAY*100/117)*0.17))/0.4558),if_else(pay$START_FIRST_PAY == "2016-11-01", (((pay$AM_FIRST_PAY - 26.43)-((pay$AM_FIRST_PAY*100/117)*0.17))/0.4558),if_else(pay$START_FIRST_PAY == "2017-01-01", (((pay$AM_FIRST_PAY - 31.81)-((pay$AM_FIRST_PAY*100/117)*0.17))/0.4726),0)))))
```





</br>









































</div>

